\noindent
\begin{longtable}{
|p{\dimexpr.30\linewidth-2\tabcolsep-1.3333\arrayrulewidth}% column 1
|p{\dimexpr.70\linewidth-2\tabcolsep-1.3333\arrayrulewidth}|% column 2
}
    \hline
    \centering \textbf{Week Commencing}        & \arraybackslash \textbf{Activities}     \\ \hline
    28/09/2020                 &
    \indent$\bullet$\ Review Summer Literature \newline
    \indent$\bullet$\ Reflect on Summer Progress \newline
    \indent$\bullet$\ Define Aims and Objectives \newline
    \indent$\bullet$\ Define a Provisional Project Plan
    \\ \hline
    05/10/2020                 &
    \indent$\bullet$\ Research Existing Maintenance Tools \newline
    \indent$\bullet$\ Research Machine Learning Techniques \newline
    \indent$\bullet$\ Research Cloud Services \newline
    \indent$\bullet$\ Learn LaTeX core elements \newline
    \indent$\bullet$\ Learn BibTeX core elements
    \\ \hline
    12/10/2020                 &
    \indent$\bullet$\ Complete Project Proposal Document \newline
    \indent$\bullet$\ Complete Project Ethics Document \newline
    \indent$\bullet$\ Create BibTex Database
    \\ \hline
    19/10/2020                 &
    \indent$\bullet$\ Write Draft Structure for Background Chapter \newline
    \indent$\bullet$\ Read Network Programming by Richard Reese \newline
    \indent$\bullet$\ Continue Learning LaTeX \newline
    \indent$\bullet$\ Continue Learning BibTeX
    \\ \hline
    26/10/2020                 &
    \indent$\bullet$\ Read Data Centres Failures paper \newline
    \indent$\bullet$\ Read Data Science Made Easy by Richard Reese \newline
    \indent$\bullet$\ Create Thesis Structure using LaTeX
    \\ \hline
    02/11/2020                 &
    \indent$\bullet$\ Write First Draft for the Background Chapter \newline
    \indent$\bullet$\ Read Computer Systems Maintenance Solutions paper \newline
    \indent$\bullet$\ Read Support Vector Machines paper \newline
    \indent$\bullet$\ Create Thesis Bibliography using BibBeX and LaTeX
    \\ \hline
    09/11/2020                 &
    \indent$\bullet$\ Write Second Draft for the Background Chapter \newline
    \indent$\bullet$\ Research Hardware Sensors \newline
    \indent$\bullet$\ Find Datasets related to Hard-Disks S.M.A.R.T \newline
    \indent$\bullet$\ Find Statistics related to Hard-Disks Failures \newline
    \indent$\bullet$\ Research Computer Network Architectures
    \\ \hline
    16/11/2020                 &
    \indent$\bullet$\ Write Third Draft for the Background Chapter \newline
    \indent$\bullet$\ Read Hidden Markov Model paper \newline
    \indent$\bullet$\ Read Bayesian Networks paper
    \\ \hline
    23/11/2020                 &
    \indent$\bullet$\ Research the Peer-to-Peer Network Architecture \newline
    \indent$\bullet$\ Research Client-Server Network Architecture \newline
    \indent$\bullet$\ Update Draft Structure for the Background Chapter \newline
    \indent$\bullet$\ Write Conclusions for the Background Chapter
    \\ \hline
    30/11/2020                 &
    \indent$\bullet$\ Continue Learning Java and JavaFX \newline
    \indent$\bullet$\ Research JavaFX User Interface Extensions \newline
    \indent$\bullet$\ Research Modern User Interface Designs
    \\ \hline
    07/12/2020                 &
    \indent$\bullet$\ Reflect on the Conclusions of the Background Chapter \newline
    \indent$\bullet$\ Research the Hard Disks S.M.A.R.T Indicators \newline
    \indent$\bullet$\ Research the Support Vector Machines Implementations
    \\ \hline
    14/12/2020                 &
    \indent \textit{Due to extenuating circumstances, no work was conducted this week}
    \\ \hline
    21/12/2020                 &
    \indent \textit{Due to Christmas break, no work was conducted this week}
    \\ \hline
    28/12/2020                 &
    \indent \textit{Due to Christmas break, no work was conducted this week}
    \\ \hline
    04/01/2021                 &
    \indent$\bullet$\ Consider the Background Chapter Feedback \newline
    \indent$\bullet$\ Edit the Background Chapter
    \\ \hline
    11/01/2021                 &
    \indent$\bullet$\ Write Specifications Chapter Introduction \newline
    \indent$\bullet$\ Write Desktop Application Functional Requirements\newline
    \indent$\bullet$\ Write Agent Application Functional Requirements\newline
    \indent$\bullet$\ Write Non-Functional Requirements
    \\ \hline
    18/01/2021                 &
    \indent$\bullet$\ Reflect on the Background and Specifications Chapters \newline
    \indent$\bullet$\ Create Unified Modeling Language Diagrams for the Desktop Application \newline
    \indent$\bullet$\ Create Unified Modeling Language Diagrams for the Agent Application
    \\ \hline
    25/01/2021                 &
    \indent$\bullet$\ Deliver First Proof of Concept Video \newline
    \indent$\bullet$\ Reflect on the intended implementation
    \\ \hline
    01/02/2021                 &
    \indent$\bullet$\ Research Hard-Disk S.M.A.R.T Data Retrieval Tools \newline
    \indent$\bullet$\ Research Java Reflection API in order to retrieve hard-disk S.M.A.R.T data. \newline
    \indent$\bullet$\ Select smartmontools third-party software to retrieve hard-disk S.M.A.R.T data. \newline
    \indent$\bullet$\ Implement hard-disk S.M.A.R.T data retrieval feature using smartmontools and Java Reflection.
    \\ \hline
    08/02/2021                 &
    \indent$\bullet$\ Research Hard-Disk S.M.A.R.T available datasets \newline
    \indent$\bullet$\ Research Machine Learning algorithms used with hard-disk S.M.A.R.T data. \newline
    \indent$\bullet$\ Select BackBlaze dataset from 2017 for the Seagate ST4000DM000 hard-disk model. \newline
    \indent$\bullet$\ Implement static analysis of the hard-disk S.M.A.R.T using Support Vector Machines.
    \\ \hline
    15/02/2021                 &
    \indent$\bullet$\ Continue Research of Machine Learning algorithms used with hard-disk S.M.A.R.T data. \newline
    \indent$\bullet$\ Implement static analysis of the hard-disk S.M.A.R.T using Random-Forest Model.
    \indent$\bullet$\ Implement static analysis of the hard-disk S.M.A.R.T using Logistic Regression.
    \indent$\bullet$\ Create Second Proof of Concept Video.
    \\ \hline
    22/02/2021                 &
    \indent$\bullet$\ Continue Research of Machine Learning algorithms used with hard-disk S.M.A.R.T data. \newline
    \indent$\bullet$\ Implement static analysis of the hard-disk S.M.A.R.T using Multi-Layer Perceptron. \newline
    \indent$\bullet$\ Create ROC Curve Figures for the machine learning algorithms.
    \\ \hline
    01/03/2021                 &
    \indent$\bullet$\ Create Final Report Structure. \newline
    \indent$\bullet$\ Write Final Report Credits using the licenses of the libraries used. \newline
    \indent$\bullet$\ Reflect on the implementation of the hard-disk S.M.A.R.T data retrieval.
    \\ \hline
    08/03/2021                 &
    \indent$\bullet$\ Research Java Bytecode manipulation libraries. \newline
    \indent$\bullet$\ Read ASM Java Bytecode manipulation library documentation. \newline
    \indent$\bullet$\ Implement validation for the authentication system of the Desktop Application. \newline
    \indent$\bullet$\ Implement Dynamic Java Archive (.jar) creation for the client application.
    \\ \hline
    15/03/2021                 &
    \indent$\bullet$\ Research Modern Designs for Dashboards. \newline
    \indent$\bullet$\ Implement Dashboard component of the interface for the Desktop Application. \newline
    \indent$\bullet$\ Implement Robert Gordon University theme for the Desktop Application.
    \\ \hline
    22/03/2021                 &
    \indent \textit{Due to extenuating circumstances, no work was conducted this week}
    \\ \hline
    29/03/2021                 &
    \indent \textit{Due to extenuating circumstances, no work was conducted this week}
    \\ \hline
    05/04/2021                 &
    \indent$\bullet$\ Research Poster Designs \newline
    \indent$\bullet$\ Create Project Poster \newline
    \indent$\bullet$\ Reflect on the Project Poster Design.
    \\ \hline
    12/04/2021                 &
    \indent$\bullet$\ Write Design Chapter of the Desktop Application and Agent \newline
    \indent$\bullet$\ Write Implementation Chapter of the Desktop Application \newline
    \indent$\bullet$\ Write Tests of the Desktop Application and Agent
    \\ \hline
    19/04/2021                 &
    \indent$\bullet$\ Write Implementation Chapter of the Agent Application \newline
    \indent$\bullet$\ Write Evaluation Chapter \newline
    \indent$\bullet$\ Write Conclusions Chapter \newline
    \indent$\bullet$\ Write Project Credits.
    \\ \hline
    26/04/2021                 &
    \indent$\bullet$\ Create PowerPoint Presentation for the Demo \newline
    \indent$\bullet$\ Final Report Modifications \newline
    \indent$\bullet$\ Submission.
    \\ \hline
\end{longtable}
\captionof{table}{Project Log}
